---
title: "BNA Report"
output:
  html_notebook:
    highlight: haddock
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
knitr::read_chunk(
  "../scripts/analysis.R"
)
```

# Case Study: `r sa_name` {.tabset}

## Analysis summary

```{r database, include = FALSE}
db_name = "bna_europe"
local_host = "localhost"
port_num = 5432
user_name = "postgres"
db_pass = rstudioapi::askForPassword("Database password")
```

```{r variables, warning = FALSE, include = FALSE}
## Basic variables to set 
country = "UK" # Possible options: UK, US (not yet), Netherlands, NA
sa_name = "Corby" # study area
sa_crs = 3857 # crs
biking_distance = 3000 ## in meters

area_type = "osm" ## possible options: 
                  ## "osm" for any country
                  ## "ttwa" for the UK

min_area = "lsoa" ## possible options: 
                  ## "geostat" for any country, 
                  ## "lsoa" or "msoa" for the UK
                  ## "cb" for the US (not yet)
                  ## "buurt" for the Netherlands

## If the analysis runs with the GEOSTAT population grid as min_area
subdivisions = 4
```

* You calculated the BNA score for 
<span style="color:#BB616D">**`r sa_name`, `r country`**</span> 
within a biking distance of 
<span style="color:#BB616D">**`r biking_distance/1000`**</span> km. 

* `r ifelse(area_type == "osm",paste("The size of the osm data for your study area is", round(osm_size,2), "MB and the"),"The")` analysis took **`r paste(round(as.numeric(duration),2), units(duration))`** to run.

* The analysis corresponds to the 
<span style="color:#BB616D">**`r ifelse(area_type == "ttwa","Travel to Work Area","OSM boundary area")`**</span> (red) based on 
<span style="color:#BB616D">**`r ifelse(min_area == "msoa","its Middle Layer Superoutput Areas (MSOA)",ifelse(min_area == "lsoa","its Lower Layer Superoutput Areas (LSOA)",ifelse(min_area == "cb","its census blocks",ifelse(min_area == "buurt","its neighborhood areas","a subdivided population grid from GEOSTAT"))))`**</span> (green).

```{r connection, include=FALSE, cache = FALSE}
```

```{r area, include=FALSE, cache = FALSE}
```

```{r verify_area, include = FALSE, echo = FALSE}
library(tmap)
tmap_mode("view")
qtm(boundary, borders = "red", borders.lwd = 3, fill = NULL, basemaps = "OpenStreetMap")
```

```{r fetch, include = FALSE, cache = FALSE}
```

```{r network, include = FALSE, cache = FALSE}
```

```{r min_area, include = FALSE, cache = FALSE}
```

```{r plot_area, fig.width = 8, fig.height= 5, echo = FALSE, warning = FALSE, message = FALSE}
library(tmap)

tmap_mode("view")
tmap_leaflet(
     tm_view(
     basemaps = "CartoDB.Positron"
   ) +
     tm_shape(min_area_grid) +
     tm_polygons(
       border.col = "green",
       alpha = 0
      ) +
     tm_shape(boundary) +
     tm_polygons(
       border.col = "red",
       alpha = 0,
       lwd = 4
      ) 
)
```

```{r reachable_roads, include = FALSE, cache = FALSE}
```

```{r accessibility, include = FALSE, cache = FALSE}
```

```{r overall_score, include = FALSE, cache = FALSE}
```

## Results

```{r data_plot, include = FALSE, warning = FALSE, echo = FALSE, cache = FALSE}
```

```{r, fig.width = 10, fig.height= 5, fig.align = 'center', echo = FALSE, warning = FALSE}
int_map <- 
  tmap::tmap_leaflet(
     tmap::tm_view(
     basemaps = c(
       "CartoDB.Positron",
       "CartoDB.DarkMatter",
       "OpenStreetMap.Mapnik"
     )
   ) +
     tmap::tm_shape(bna_score) +
     tmap::tm_polygons(
       col = "overall_score",
       style = "fixed",
       breaks = bna_breaks,
       palette = bna_pal,
       alpha = 0.8,
       title = "BNA score",
       border.col = NULL,
       colorNA = NULL,
       showNA = FALSE, 
       id = "bna_popup"
      ) +
     tmap::tm_shape(stress_network) +
     tmap::tm_lines(
       col = "ft_stress", 
       colorNA = NULL,
       showNA = FALSE,
       palette = c("firebrick1", "deepskyblue3"),
       title.col = "Stress network"
      ) +
     tmap::tm_shape(stress_network) +
     tmap::tm_lines(
       col = "tf_stress", 
       colorNA = NULL,
       showNA = FALSE,
       palette = c("firebrick1", "deepskyblue3"),
       legend.col.show = FALSE
      )
  )

int_map
```

```{r display_table, include = TRUE, echo = FALSE, cache = FALSE}
```

```{r duration, include = FALSE, cache = FALSE}
```
